Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-05 paper/paper.tex
Extended introduction.

\section{Introduction}
\begin{comment}
The use of the internet has become an almost unavoidable part of life. As the internet becomes more involved with everyday life, users put more and more of their personal information online. Phishing is the process of stealing, gaining access to, or recording personal accounts or information. Phishing attacks try to convince the target to give up personal information such as passwords, account names, credit card numbers, addresses, and other valuable information or credentials. Phishing has many mediums such as email, phone, websites, and even mail. This information can be used in a variety of destructive ways from the thievery of personal assets to identity theft. Tabnabbing is a specific phishing technique that relies on the user’s trust of websites they have already viewed and considered safe. Some users often leave many tabs open to return to interesting websites at a later time and this behavior makes those users the perfect target for this type of attack. When the user is not has left a tab a malicious webesite can detect that the user is not currently viewing that tab and change the content of that page. This is done using JavaScript or by using the meta tag with a timer to redirect the page at a time when the user is most likely not viewing it. An example of one such change is making the page apear to be the gmail login page in the hopes that the user will atempt to login giving the malicious site the username and password for the unsuspecting user. Phishing attacks are becoming more common as web use increases, and as users become more aware of phishing attacks, phishing techniques adapt to continue to be effective. Tabnabbing is one such new technique that has emerged recently and is effective even against users that have been trained to only give sensitive information to trusted websites.
\end{comment}

>>>>

\section{Introduction}
The use of the Internet has become an almost unavoidable part of life. As the Internet becomes more involved with everyday life, users put more and more of their personal information online. Phishing is the process of stealing, gaining access to, or recording personal accounts or information. Phishing attacks try to convince the target to give up personal information such as passwords, account names, credit card numbers, addresses, and other valuable information or credentials. Phishing has many mediums such as email, phone, websites, and even mail. This information can be used in a variety of destructive ways from the thievery of personal assets to identity theft.  However, the large and constantly looming threat of phishing attacks have caused many users to become perpetually cautious when visiting new and unfamiliar sites.

Phishing attacks are always developing and evolving, and one particular type of attack attempts to trick the user well after they have initially visited the site.  Tabnabbing is a specific phishing technique that relies on the user’s trust of websites they have already viewed and considered safe. Some users often leave many tabs open to return to interesting websites at a later time, and this behavior makes those users the perfect target for this type of attack. When the user has left a tab, a malicious website can detect that the user is not currently viewing that tab and change the content of that page. This is done using JavaScript or the HTML meta tag with a timer to redirect the page at a time when the user is most likely not viewing it. The malicious site will typically attempt to change the site to appear as a login page for a familiar site such as Gmail or Facebook.  When the user returns to the tab, the changed page may request the user for their username and password, citing reasons such as an expired login session.  Because tabs are not expected to have changed while out-of-focus, and because users do not check URLs often, the site will seem legitimate, and the user will be less cautious because the tab was not newly created.

\begin{comment}

Phishing attacks are becoming more common as web use increases, and as users become more aware of phishing attacks, phishing techniques adapt to continue to be effective. Tabnabbing is one such new technique that has emerged recently and is effective even against users that have been trained to only give sensitive information to trusted websites.
\end{comment}
